Plant-pollintor networks worldwide are composed by the same specific building

### 2021-10-10 Draft/Draft.Rmd
Starting with the discussion, I keep after lunch

The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a `r over`% and `r under`% of over- (>75$^{th}$) and under- (<25th) represented functional groups in the different positions, respectively (**Figure 3**). Floral visitors showed a total of `r poll_over_75`% and `r poll_under_25`% of over- and under-represented functional groups in the different positions and plants `r plant_over_75`% and `r plant_under_25`% of over and under-represented, respectively. Notably, the differences across functional groups were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors). From most over- to under-represented floral visitors functional groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera. Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.

[IB: De aqui hay que sacar un ejemplo para el abstract. No hace falta que este en los resultados, pero sí podemos usarlo en la discusión. Por ejemplo. Bees and self icop. perenials are over repsented in fan positions, while ...]()
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="90%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions. The different motif positions are dividied by the average path length clasification determined by Simmons et al. (2020). The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}

@@

[IB: Me pregunto si el ultimo parrafo es mejor meterlo aquí, por que de hecho, la figura 4 son las expected probabilities, no? Se podria empezar diciendo eso, y meter la figura de expected probabilities]()

@@

[IB: Me falta un take home message. Yo creo que es que no podemos predecir las combinciones por sus probabilidades y eso es muy bestia! Lo he añadido ya al inicio de este parrafo, pero dejo el comentario por que es un paper complejo y hay que guiar mucho. Cada sección deberia tener un mensage claro ( y ese it a abstract) 1) Los motifs no son al azar. 2) hay posiciones usadas principalmente por ciertos FG. 3) Hay combinaciones de FG que van más alla de pura probabilidad. Fin.]()

@@

Alfonso (comentario después de fig 5 donde tenía remarkably y ahora un in addition): Yo creo que todo esto es expected. Sin embargo, las explicaciones de por qué lo es probablemente van en la discusión. Lo mismo que el ajuste de la Johnson's SU: la cola larga de la derecha la producen la sobreabundancia de motifs de 4 y 5 nodos, en comparación con los de 3.
---

@@

>>>>

The comparison of the functional group frequencies per motif position between empirical and simulated networks showed a `r over`% and `r under`% of over- (>75$^{th}$) and under- (<25th) represented functional groups in the different positions, respectively (**Figure 3**). Floral visitors showed a total of `r poll_over_75`% and `r poll_under_25`% of over- and under-represented functional groups in the different positions and plants `r plant_over_75`% and `r plant_under_25`% of over and under-represented groups, respectively. Notably, the differences across functional groups were more marked for floral visitors than for plant functional groups (the differences between min and max percentiles per position were generally two-three times larger for floral visitors). From most over- to under-represented floral visitors functional groups on the different motif positions (indicated with the dendrogram order in **Figure 3**), we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee Hymenoptera and Lepidoptera. Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.

---
THIS IS A COMMENT
IB: De aqui hay que sacar un ejemplo para el abstract. No hace falta que este en los resultados, pero sí podemos usarlo en la discusión. Por ejemplo. Bees and self icop. perenials are over repsented in fan positions, while ...
---

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="80%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions. The different motif positions are dividied by the average path length clasification determined by Simmons et al. (2020). The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}

@@

@@

@@

Alfonso (comentario después de fig 5 donde tenía remarkably y ahora un in addition): Yo creo que todo esto es expected. Sin embargo, las explicaciones de por qué lo es probablemente van en la discusión. Lo mismo que el ajuste de la Johnson's SU: la cola larga de la derecha la producen la sobreabundancia de motifs de 4 y 5 nodos, en comparación con los de 3.

IB: Me falta un take home message. Yo creo que es que no podemos predecir las combinciones por sus probabilidades y eso es muy bestia! Lo he añadido ya al inicio de este parrafo, pero dejo el comentario por que es un paper complejo y hay que guiar mucho. Cada sección deberia tener un mensage claro ( y ese it a abstract) 1) Los motifs no son al azar. 2) hay posiciones usadas principalmente por ciertos FG. 3) Hay combinaciones de FG que van más alla de pura probabilidad. Fin.
---

@@

Understanding the global patterns of network structure is key to unravel the processes that govern community dynamics [@bascompte2007; @bastolla2009; @guimaraes2020]. However, common analytical approaches are unable to capture the full complexity of ecological systems. By analysing over- and under-representation of network motifs with a comprehensive dataset of real plant-pollinator networks we have shown that motifs are consistently over- and under-represented indicating the lack of randomness of the patterns of interactions at the meso-scale. This has direct implications with
